A survey of HTTP caching options on the open Web

### 2015-01-09 sanity/paper1.tex
comment on 60%
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@958 43ef1190-90fd-4dd7-a769-d0121f02b80e

We were able to compute a heuristic lifetime for 554 resources, a
larger number than standards-compliant resources. In Figure\todo{add all
  heuristics figure}, we see that the distribution of lifetimes are
radically different from the case in Figure\todo{ref fig:allhard}. In
this case, we may cache many resources for months. Only a handful of
resources had changed in the last minutes. Since this is based
on actual times since last modifications, this suggests that many
resources should have had explicit cache headers with very long
lifetimes. \todo{compare Jürgen and LD observatory}

>>>>

We were able to compute a heuristic lifetime for 554 resources, a
larger number than standards-compliant resources. In Figure\todo{add all
  heuristics figure}, we see that the distribution of lifetimes are
radically different from the case in Figure\todo{ref fig:allhard}. In
this case, we may cache many resources for months. Only a handful of
resources had changed in the last minutes. Since this is based
on actual times since last modifications, this suggests that many
resources should have had explicit cache headers with very long
lifetimes. This is supported by DyLDO\todo{ref}, which concludes that:
\begin{quote}
[...] We found that 62.2\% of documents didn’t change over the six
months and found that 51.9\% of domains were considered static.
\end{quote}
This agrees well with that 60\% of the simple heuristic lifetimes are
in the month range.
